Sound Automated Synthesis of Digital Controllers

### 2016-10-08 paper/paper.tex
hscc17

Since $G(z)$ is an approximation of $G(s)$ we denote the error in the
approximation for time $t \neq kT$ as $\Delta{G}_P$
%
\begin{align}
\small
\label{parametric_plant_tf}
\hat{G}(z)&=\frac{(b_{0}+\Delta_p b_{0}) +...+(b_{M_G}+\Delta_p b_{M_G})z^{-M_G}}{(a_{0}+\Delta_p a_{0})+...+(a_{N_G}+\Delta_p a_{N_G})z^{-N_G}} \nonumber \\
&=G(z)+\Delta{G}_P(z).
\end{align}
%
Note that $\Delta{G}_P$ is undefined and upperbound by a user defined
percentage such that $\hat{G}(z)$ corresponds to the polynomial set of
possible values of $G(z, T): \forall T \in \mathbb{R}$

Let $\tilde C(z)$ and $\tilde G(z)$ be the transfer functions represented
using a Fixed Point Finite Word Length with integer size $I$ and fractional
size $F$.  We shall denote this domain as $\mathbb{R}\langle I,F \rangle$
%
\begin{align}
\small
\label{digital_controller_plant_tf}
\tilde C(z)&=\frac{\tilde \beta_{0}+\tilde \beta_{1}z^{-1}+...+\tilde \beta_{M_C}z^{-M_C}}{\tilde \alpha_{0}+\tilde \alpha_{1}z^{-1}+...+\tilde \alpha_{N_C}z^{-N_C}}, \\
%\label{plant_tf}
\tilde G(z)&=\frac{\tilde b_{0}+\tilde b_{1}z^{-1}+...+\tilde b_{M_G}z^{-M_G}}{\tilde a_{0}+\tilde a_{1}z^{-1}+...+\tilde a_{N_G}z^{-N_G}}.
\end{align}

Since the controller is implemented in the $\mathbb{R}\langle I,F \rangle$
domain,
%
 $$\forall i \leq N_C, j \leq M_C\ \  \tilde \beta_{i} \equiv \beta_{i} \wedge \tilde \alpha_{j} \equiv \alpha_{j} \Leftrightarrow \tilde C(z) \equiv C(z)$$
%
However, given a real plant and real controller $\hat{G}(z), \hat{C}(z)$,
%
\begin{align}
\small
\label{FWL_tf}
&\exists f (x \in \mathbb{R}) \rightarrow \tilde x \in \mathbb{R}\langle I,F \rangle : \\
\label{digital_controller_tf}
\tilde C(z)&=\frac{(\hat{\beta}_{0}+\Delta_q \hat{\beta}_{0}) +...+(\hat{\beta}_{M_C}+\Delta_q \hat{\beta}_{M_C})z^{-M_C}}{(\hat{\alpha}_{0}+\Delta_q \hat{\alpha}_{0})+...+(\hat{\alpha}_{N_C}+\Delta_q \hat{\alpha}_{N_C})z^{-N_G}} \nonumber \\
&= C(z) =\hat{C}(z) + \Delta{C}(z)\\
\label{digital_plant_tf}
\tilde G(z)&=\frac{(\hat{b}_{0}+\Delta_q \hat{b}_{0}) +...+(\hat{b}_{M_G}+\Delta_q \hat{b}_{M_G})z^{-M_G}}{(\hat{a}_{0}+\Delta_q \hat{a}_{0})+...+(\hat{a}_{N_G}+\Delta_q \hat{a}_{N_G})z^{-N_G}} \nonumber \\
&=G(z)+\Delta{G}_P(z)+\Delta{G}_Q(z).
\end{align}

\vspace{1 mm} 
\noindent where $\Delta{G}_Q(z)$ represents the plant uncertainty caused by
the rounding off effect.  We may encompass all the uncertainty as
$\Delta{G}(z)=\Delta{G}_P(z)+\Delta{G}_Q(z)$.  Since this value is
nondeterministic, the polynomial set of possible values of $\tilde G(z)$ is
denoted by $\mathfrak{G}(z)$.

@@

First, some assumptions have to be established to obtain a model for the
quantization effects (seen as noise) on the closed loop system.
%
\begin{myassumption}
\label{whitenoise}
%
The quantization noises $\nu_{1}$ (from the $Q1$) and $\nu_{2}$ (from the
$Q2$) are energy bounded uncorrelated white noises.

In~\cite{widrow1956}, Widrow models the quantization noise as a gaussian
model in which the second moment (variance) of the probability density
function (pdf) of the quantization noise is given by
%
\begin{equation}
\label{eq:variancelemma}
\sigma_{Q}^{2}=\frac{q^{2}}{12},
\end{equation}
where $q$ is the step size of quantizer, thus supporting this assumption.
\end{myassumption}

@@

%Eq.~\eqref{eq:deltag_var} indicates that the modelling of the quantization noise
%effect on the plant transfer function demands an estimation of the variance
%of quantization noise $\sigma_{Q}^{2}$.  To obtain such estimation, the
%methodology presented by~\cite{widrow2008quantization}
%is used.  The authors provide an algorithm for computing the mean square of
%the output noise due to $Q1$ and $Q2$.  Considering that each quantizer
%contribution can be represented by a white noise with zero mean
%(Assumption~\ref{whitenoise}), the mean square can be considered as the
%variance of noise ($\sigma_{Q}^{2}$), which can be calculated as
%%
%\begin{equation}
%\sigma_{Q}^{2}=\frac{\lambda_{1}^{2}\cdot \sum {h_{Q1}^{2}} \cdot q_{1}+\lambda_{2}^{2}\cdot \sum {h_{Q2}^{2}} \cdot q_{2}}{12},
%\end{equation}
%%
%\noindent where $\lambda_{1}$ and $\lambda_{2}$ are the scale factors, {\it i.e.} constant gains usually employed before the ADC and after the DAC in order to avoid the overload of converters  %\red{[define scale factors]} 
%for the quantization $Q1$ and $Q2$, respectively; $q_{1}$ and $q_{2}$ are the quantization step for $Q1$ and $Q2$, respectively, and $\sum {h_{Q1}^{2}}$ and $\sum
%{h_{Q2}^{2}}$ are the squares sums of the impulse response obtained by means
%of a transfer function from $Q1$ and $Q2$ to the plant output, respectively.
%
%The transfer functions $H_{Q1}(z)$ and $H_{Q2}(z)$, from which the squares
%sums of the impulse response are needed, can be obtained through the
%analysis of the system in Figure~\ref{fig:sampledsystem}. 
Considering that
the quantizer $Q1$ is the source of a white noise with zero mean $\nu_{1}$
and $Q2$ is the source of a white noise with zero mean $\nu_{2}$, the
following equation can be written for the system in
Figure~\ref{fig:sampledsystem}
%
\begin{equation}
\resizebox{0.48\textwidth}{!}{
$\hat{Y}(z)=\nu_{1}(z)C(z)G(z)+\nu_{2}(z)G(z)+R(z)C(z)G(z)-\hat{Y}(z)C(z)G(z),$
}
\end{equation}

@@

\paragraph{General architecture of the program synthesiser}
%
%% \red{[I would recommend to clarify the domain of definition of $\sigma$, particularly over the set where $x$ ranges over. 
%% (Be cognisant that control audience might be unfamiliar with the cegis architecture.) ]}
% 
The input specification provided to the program synthesiser is of the
form $\exists \vec{P} . \forall \vec{x} \in \text{\sc inputs}
. \sigma(\vec{x}, \vec{P})$ where $\vec{P}$ ranges over functions,
$\vec{x}$ ranges over ground terms and $\sigma$ is a quantifier-free
formula.  We interpret the gound terms over some finite domain
$\mathcal{D}$.

>>>>

Since $G(z)$ is an approximation of $G(s)$ \red{we denote [AA: why `denote'? Shouldn't we prove that we go from the $G(s)$ TF to the $G(z,T)$ form above?]} the error in the
approximation for time $t \neq kT$ as $\Delta{G}_P$
%
\begin{align}
\small
\label{parametric_plant_tf}
\hat{G}(z)&=\frac{(b_{0}+\Delta_p b_{0}) +...+(b_{M_G}+\Delta_p b_{M_G})z^{-M_G}}{(a_{0}+\Delta_p a_{0})+...+(a_{N_G}+\Delta_p a_{N_G})z^{-N_G}} \nonumber \\
&=G(z)+\Delta{G}_P(z).
\end{align}
%
Note that $\Delta{G}_P$ is undefined and upperbound by a user defined
percentage such that $\hat{G}(z)$ corresponds to the polynomial set of
possible values of $G(z, T): \forall T \in \mathbb{R}$. 
\red{[The previous statement is confusing and I must disagree here: I want hard error bounds on a specific value of T.]}

Let $\tilde C(z)$ and $\tilde G(z)$ be the transfer functions represented
using a Fixed-Point Finite Word Length with integer size $I$ and fractional
size $F$.  We shall denote this domain as $\mathbb{R}\langle I,F \rangle$ and obtain 
%
\begin{align}
\small
\label{digital_controller_plant_tf}
\tilde C(z)&=\frac{\tilde \beta_{0}+\tilde \beta_{1}z^{-1}+...+\tilde \beta_{M_C}z^{-M_C}}{\tilde \alpha_{0}+\tilde \alpha_{1}z^{-1}+...+\tilde \alpha_{N_C}z^{-N_C}}, \\
%\label{plant_tf}
\tilde G(z)&=\frac{\tilde b_{0}+\tilde b_{1}z^{-1}+...+\tilde b_{M_G}z^{-M_G}}{\tilde a_{0}+\tilde a_{1}z^{-1}+...+\tilde a_{N_G}z^{-N_G}}.
\end{align}

Since the controller is implemented in the $\mathbb{R}\langle I,F \rangle$
domain,
%
 $$\forall i \leq N_C, j \leq M_C\ \  \tilde \beta_{i} \equiv \beta_{i} \wedge \tilde \alpha_{j} \equiv \alpha_{j} \Leftrightarrow \tilde C(z) \equiv C(z)$$
%
However, given a real plant and real controller $\hat{G}(z), \hat{C}(z)$, 
\red{[the first line is not clear, there is in particular a function that is left undefined.]}
%
\begin{align}
\small
\label{FWL_tf}
&\exists f (x \in \mathbb{R}) \rightarrow \tilde x \in \mathbb{R}\langle I,F \rangle : \\
\label{digital_controller_tf}
\tilde C(z)&=\frac{(\hat{\beta}_{0}+\Delta_q \hat{\beta}_{0}) +...+(\hat{\beta}_{M_C}+\Delta_q \hat{\beta}_{M_C})z^{-M_C}}{(\hat{\alpha}_{0}+\Delta_q \hat{\alpha}_{0})+...+(\hat{\alpha}_{N_C}+\Delta_q \hat{\alpha}_{N_C})z^{-N_G}} \nonumber \\
&= C(z) =\hat{C}(z) + \Delta{C}(z)\\
\label{digital_plant_tf}
\tilde G(z)&=\frac{(\hat{b}_{0}+\Delta_q \hat{b}_{0}) +...+(\hat{b}_{M_G}+\Delta_q \hat{b}_{M_G})z^{-M_G}}{(\hat{a}_{0}+\Delta_q \hat{a}_{0})+...+(\hat{a}_{N_G}+\Delta_q \hat{a}_{N_G})z^{-N_G}} \nonumber \\
&=G(z)+\Delta{G}_P(z)+\Delta{G}_Q(z).
\end{align}
\red{[please, how can you claim that the error enters as written? Can you show the derivation? Can you show a reference that has derived this form?]}
where $\Delta{G}_Q(z)$ represents the plant uncertainty caused by
the rounding off effect.  We may encompass all the uncertainty as
$\Delta{G}(z)=\Delta{G}_P(z)+\Delta{G}_Q(z)$.  Since this value is
nondeterministic, the polynomial \red{[why polynomial?]} set of possible values of $\tilde G(z)$ is
denoted by $\mathfrak{G}(z)$.

@@

First, some assumptions have to be established to obtain a model for the
quantization effects (seen as noise) on the closed loop system.
%
\begin{myassumption}
\label{whitenoise}
%
The quantization noises $\nu_{1}$ (from the $Q1$) and $\nu_{2}$ (from the
$Q2$) are energy bounded uncorrelated white noises.
% 
In particular, \cite{widrow1956} models the quantization noise as a gaussian
model in which the second moment (variance) of the probability density
function (pdf) of the quantization noise is given by
%
\begin{equation}
\label{eq:variancelemma}
\sigma_{Q}^{2}=\frac{q^{2}}{12},
\end{equation}
where $q$ is the step size of quantizer. 
%, thus supporting this assumption.
\end{myassumption}

@@

%Eq.~\eqref{eq:deltag_var} indicates that the modelling of the quantization noise
%effect on the plant transfer function demands an estimation of the variance
%of quantization noise $\sigma_{Q}^{2}$.  To obtain such estimation, the
%methodology presented by~\cite{widrow2008quantization}
%is used.  The authors provide an algorithm for computing the mean square of
%the output noise due to $Q1$ and $Q2$.  Considering that each quantizer
%contribution can be represented by a white noise with zero mean
%(Assumption~\ref{whitenoise}), the mean square can be considered as the
%variance of noise ($\sigma_{Q}^{2}$), which can be calculated as
%%
%\begin{equation}
%\sigma_{Q}^{2}=\frac{\lambda_{1}^{2}\cdot \sum {h_{Q1}^{2}} \cdot q_{1}+\lambda_{2}^{2}\cdot \sum {h_{Q2}^{2}} \cdot q_{2}}{12},
%\end{equation}
%%
%\noindent where $\lambda_{1}$ and $\lambda_{2}$ are the scale factors, {\it i.e.} constant gains usually employed before the ADC and after the DAC in order to avoid the overload of converters  %\red{[define scale factors]} 
%for the quantization $Q1$ and $Q2$, respectively; $q_{1}$ and $q_{2}$ are the quantization step for $Q1$ and $Q2$, respectively, and $\sum {h_{Q1}^{2}}$ and $\sum
%{h_{Q2}^{2}}$ are the squares sums of the impulse response obtained by means
%of a transfer function from $Q1$ and $Q2$ to the plant output, respectively.
%
%The transfer functions $H_{Q1}(z)$ and $H_{Q2}(z)$, from which the squares
%sums of the impulse response are needed, can be obtained through the
%analysis of the system in Figure~\ref{fig:sampledsystem}.

\red{[The following text needs to be completed. (Notice typos, reference to wrong signal $R$, and to wrong TF $C,G$.]}

Considering that
the quantizer $Q1$ is the source of a white noise with zero mean $\nu_{1}$
and $Q2$ is the source of a white noise with zero mean $\nu_{2}$, the
following equation can be written for the system in
Figure~\ref{fig:sampledsystem}
%
\begin{equation}
\resizebox{0.48\textwidth}{!}{
$\hat{Y}(z)=\nu_{1}(z)C(z)G(z)+\nu_{2}(z)G(z)+R(z)C(z)G(z)-\hat{Y}(z)C(z)G(z),$
}
\end{equation}

@@

\paragraph{General architecture of the program synthesiser}
%
%% \red{[I would recommend to clarify the domain of definition of $\sigma$, particularly over the set where $x$ ranges over. 
%% (Be cognisant that control audience might be unfamiliar with the cegis architecture.) ]}
% 
The input specification provided to the program synthesiser is of the
form $\exists \vec{P} . \forall \vec{x} \in \text{\sc inputs}
. \sigma(\vec{x}, \vec{P})$ where $\vec{P}$ ranges over functions,
$\vec{x}$ ranges over ground terms and $\sigma$ is a quantifier-free
formula.  We interpret the ground terms over some finite domain
$\mathcal{D}$.
